---
title: "GNBF6010 seruat"
output:
  html_document:
    df_print: paged
  word_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
setwd("C:/Users/may/Desktop/keti")
# save wanted RData in a file
# save(data, pbmc, all.genes, file = "my.RData")
# or save all data
# save.image(file="allData")
library(Seurat)
library(dplyr)
library(patchwork)
library("data.table")
library(scuttle)
library(ggplot2)
memory.limit(size=100000000)
# Load the RData
#load("C:/Users/may/Desktop/keti/D.RData")
```

```{r}
# Load the PBMC dataset
data <- readSparseCounts('data.raw.matrix.txt')
data[100:200,]

# Initialize the Seurat object with the raw (non-normalized data).
pbmc <-CreateSeuratObject(counts = data, project = "pbmc3k", min.cells = 3, min.features = 200)
pbmc
head(pbmc@meta.data)
```

Pre-processing
QC metrics
The [[ operator can add columns to object metadata. This is a great place to stash QC stats
```{r}
pbmc[["percent.mt"]] <- PercentageFeatureSet(pbmc, pattern = "^MT-")
head(pbmc@meta.data,10)
pbmc[["RNA"]]@counts[c("CD3D", "TCL1A", "MS4A1"), 1:30]
```

Visualize QC metrics as a violin plot
```{r}
VlnPlot(pbmc, features = "nFeature_RNA") & geom_hline(yintercept = 200)
```

FeatureScatter is typically used to visualize feature-feature relationships, but can be used
for anything calculated by the object, i.e. columns in object metadata, PC scores etc.
```{r}
plot1 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "percent.mt")
plot2 <- FeatureScatter(pbmc, feature1 = "nCount_RNA", feature2 = "nFeature_RNA")
plot1 + plot2
pbmc <- subset(pbmc, subset = nFeature_RNA > 200 & nFeature_RNA < 2500 & percent.mt < 5)
```

Normalizing the data
```{r}
pbmc <- NormalizeData(pbmc, normalization.method = "LogNormalize", scale.factor = 10000)
# or: pbmc <- NormalizeData(pbmc)
#normalized.data <- pbmc[["RNA"]]@data
#normalized.data[1:10,1:2]
```

Feature selection
```{r}
pbmc <- FindVariableFeatures(pbmc, selection.method = "vst", nfeatures = 2000)

# Identify the 10 most highly variable genes
top10 <- head(VariableFeatures(pbmc), 10)

# plot variable features with and without lab
plot1 <- VariableFeaturePlot(pbmc)
plot2 <- LabelPoints(plot = plot1, points = top10, repel = TRUE)
plot1 + plot2
```

Data scaling
```{r}
all.genes <- rownames(pbmc)
pbmc <- ScaleData(pbmc, features = all.genes)
#scale.data <- pbmc[["RNA"]]@scale.data
#scale.data[1:10,1:4]
#rm(scale.data)
```

Perform linear dimensional reduction
```{r}
pbmc <- RunPCA(pbmc, features = VariableFeatures(object = pbmc))
```

Determine the ‘dimensionality’ of the dataset
```{r}
# NOTE: This process can take a long time for big datasets, comment out for expediency. More
# approximate techniques such as those implemented in ElbowPlot() can be used to reduce
# computation time
pbmc <- JackStraw(pbmc, num.replicate = 100)
pbmc <- ScoreJackStraw(pbmc, dims = 1:20)
JackStrawPlot(pbmc, dims = 1:20)
ElbowPlot(pbmc)
```

Cluster the cells
```{r}
pbmc <- FindNeighbors(pbmc, dims = 1:6)
pbmc <- FindClusters(pbmc, resolution = 0.4)
head(Idents(pbmc), 5)
```

Run non-linear dimensional reduction (tSNE)
```{r}
pbmc <- RunTSNE(pbmc, dims = 1:6)
png(file = "fig1.png")
DimPlot(pbmc, reduction = "tsne")
dev.off()
```
Finding differentially expressed features (cluster biomarkers)
# find all markers of cluster 2
```{r}
cluster3.markers <- FindMarkers(pbmc, ident.1 = 3, min.pct = 0.25)
head(cluster3.markers, n = 5)
```
# find all markers distinguishing cluster 5 from clusters 0 and 3
```{r}
cluster5.markers <- FindMarkers(pbmc, ident.1 = 5, ident.2 = c(0, 3), min.pct = 0.25)
head(cluster5.markers, n = 5)
```
# find markers for every cluster compared to all remaining cells, report only the positive ones
```{r}
pbmc.markers <- FindAllMarkers(pbmc, only.pos = TRUE, min.pct = 0.25, logfc.threshold = 0.25)
pbmc.markers %>%
    group_by(cluster) %>%
    slice_max(n = 2, order_by = avg_log2FC)
```

# plot the expression level of some special genes
```{r}
VlnPlot(pbmc, features = c("MS4A1", "CD79A"))
```

Different Marker genes
```{r}
# T cell
FeaturePlot(pbmc, features = c( "CD3D","CD3E","CD2")) 
# Monocytic
FeaturePlot(pbmc, features = c( "CD14","CD68","LYZ","FCGR3A"))
# Luminal
FeaturePlot(pbmc, features = c( "AR","KRT18","KRT8"))
# Basal/intermediate
FeaturePlot(pbmc, features = c( "KRT14","KRT5"))
# Fibroblast
FeaturePlot(pbmc, features = c( "COL3A1","COL1A1")) 
# B cell
FeaturePlot(pbmc, features = c( "MS4A1","CD79A"))
# Endothelial
FeaturePlot(pbmc, features = c( "ENG","VWF"))
# Mast
FeaturePlot(pbmc, features = c( "MS4A2","TPSAB1","TPSB2"))
FeaturePlot(pbmc, features = c("CD3D", "CD79A", "C1QA", "CD163", "EPCAM", "PECAM1", "VIM", "DCN","S100A9"), pt.size=0.01)
```

Annotate cell types by SingleR tool
```{r}
if (!require("BiocManager", quiet = TRUE))
    install.packages("BiocManager")

BiocManager::install("BiocParallel")

library(celldex)
ref <- HumanPrimaryCellAtlasData()
library(SingleR)
library(BiocParallel)

pred.scRNA <- SingleR(test = pbmc@assays$RNA@data, ref = ref, labels = ref$label.main,clusters = pbmc@active.ident)

#See the labels
pred.scRNA$pruned.labels
```

Assigning cell type identity to clusters
```{r}
levels(pbmc)
new.cluster.ids <- c("Luminal", "Luminal","Luminal","T cell","Luminal","Endothelial","Luminal","Monocytic","Fibroblast","Luminal","Mast","Basal/Intermediate","Luminal","B cell","Chondrocyte","Endothelial")

pbmc@active.ident

names(new.cluster.ids) <- levels(pbmc)
pbmc <- RenameIdents(pbmc, new.cluster.ids)
levels(pbmc)

# tSNE plot of annotated cell clusters
pbmc <- RunTSNE(pbmc, dims = 1:6)
png(file = "fig2.png")
DimPlot(pbmc, reduction = "tsne", label = TRUE)+ NoLegend() + scale_color_manual(values = c("#00DDA2","deeppink","goldenrod","purple","#33FF33","#00A9FF","red","yellow","gray"))
dev.off()
```

Dot plot of gene marker expression of different cell types
```{r}
features<-c('ACTA2','PECAM1','VWF','ENG','CMA1','MS4A2','TPSAB1','TPSB2','AR','KRT19','KRT18','KRT8','TP63','KRT14','KRT5','LYZ','FCGR3A','CSF1R','CD68','CD163','CD14','UCHL1','HAVCR2','PDCD1','CTLA4','CD8A','SELL','PTPRC','CD4','BTLA','IL2RA','IL7R','CCR7','CD28','CD27','SLAMF1','DPP4','CD7','CD2','CD3G','CD3E','CD3D')
features<-rev(features)
d<-DotPlot(
  object=pbmc,
  assay = NULL,
  features,
  cols = c("lightgrey", "blue"),
  col.min = -2.5,
  col.max = 2.5,
  dot.min = 0,
  dot.scale = 6,
  idents = NULL,
  group.by = NULL,
  split.by = NULL,
  cluster.idents = TRUE,
  scale = TRUE,
  scale.by = "radius",
  scale.min = NA,
  scale.max = NA
)
j<-d+coord_flip()+theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5,size=8),axis.text.y = element_text(size=5))
j


```



```{r}
## Alternative way to assign different color to clusters
library(tidyverse)
tsne = pbmc@reductions$tsne@cell.embeddings %>%
      as.data.frame() %>% cbind(tx = pbmc@meta.data$seurat_clusters)

## 用 ggplot 绘图（假设所有的细胞被分为 6 个 cluster）
jpeg(file = "tSNE.by_cluster.jpg", width = 7, height = 7, units = "in", res = 600)
myplot <- ggplot(tsne, aes(x = tSNE_1, y = tSNE_2, color = tx)) + 
      geom_point(size = 0.2, alpha = 1) + 
      scale_color_manual(values=c("1" = "cyan3","10"="cyan3","5"= "cyan3","0" = "cyan3","9" = "cyan3","3" = "cyan3","11" = "purple",  "4" = "cyan3", "5" = "cyan3", "6" = "cyan3","7" = "cyan3","14" = "goldenrod","8"="goldenrod","13"="deepskyblue","12"="yellow green","2"="deeppink1","16"="yellow", "15" = "red"))
myplot + theme_bw()
```



Reanalysis of cell subtypes

T cell
```{r}
sce = pbmc[, Idents(pbmc) %in% c( "T cell")]
sce <- NormalizeData(sce, normalization.method = "LogNormalize", scale.factor = 1e4) 
sce <- FindVariableFeatures(sce, selection.method = 'vst', nfeatures = 2000)
all.genes <- rownames(sce)
sce <- ScaleData(sce,features = all.genes)

sce <- RunPCA(sce, features = VariableFeatures(object = sce))

sce <- FindNeighbors(sce, dims = 1:8)
sce <- FindClusters(sce, resolution = 0.4)

sce <- RunTSNE(sce, dims = 1:8)
DimPlot(sce, reduction = 'tsne',label=T)
```

Find T cell subtypes
```{r}
par(mfrow=c(2,3))
FeaturePlot(sce, features = c( "CD4","CD8A","CCR7","GZMA","FOXP3","LAG3"))

FeaturePlot(sce, features = c( "FOXP3","IL2RA","CTLA4","IKZF2","IKZF4","TNFRSF18"))

#CD8+
FeaturePlot(sce, features = c( "GZMH", "GZMB", "GZMA", "PRF1"))

#CD8+ naive
VlnPlot(sce, features = c( "CD45RA","CD62L","CD127","CDR7","CCR7","ACACB"))

#CD8+ effector
VlnPlot(sce, features = c( "CCL5"))

#CD8+
VlnPlot(sce, features = c( "KLK3"))

#CD4+
VlnPlot(sce, features = c( "CD4"))

#Treg
VlnPlot(sce, features = c( "FOXP3","CD25"),pt.size=0)

# Use SingleR to help annotate cells
if (!require("BiocManager", quiet = TRUE))
    install.packages("BiocManager")
BiocManager::install("BiocParallel")
library(celldex)
ref <- BlueprintEncodeData()
library(SingleR)
library(BiocParallel)
pre.scRNA <- SingleR(test = sce@assays$RNA@data, ref = ref, labels = ref$label.main,clusters = sce@active.ident)
pre.scRNA$pruned.labels

VlnPlot(sce, features = c("CD8A", "CD4"),pt.size=0)
VlnPlot(sce, features = c("AR"))
VlnPlot(sce, features = c("GZMH", "GZMB", "GZMA", "PRF1","IFN"))
VlnPlot(sce, features = c("KLK3"))
VlnPlot(sce, features = c("FOLH1"))
VlnPlot(sce, features = c("FOXP3","IL2RA","STAT5A","CTLA4"))
VlnPlot(sce1, features = c("CCL2"),pt.size=0)
VlnPlot(pbmc,features=c("COL3A1",'MS4A1'),pt.size=0)
```

Epithelial cell
```{r}
sce1 = pbmc[, Idents(pbmc) %in% c( "Basal/Intermediate","Luminal")]
sce1 <- NormalizeData(sce1, normalization.method = "LogNormalize", scale.factor = 1e4) 
sce1 <- FindVariableFeatures(sce1, selection.method = 'vst', nfeatures = 2000)
all.genes <- rownames(sce1)
sce1 <- ScaleData(sce1,features = all.genes)
sce1 <- RunPCA(sce1, features = VariableFeatures(object = sce1))

sce1 <- FindNeighbors(sce1, dims = 1:9)
sce1 <- FindClusters(sce1, resolution = 0.4)

sce1 <- RunTSNE(sce1, dims = 1:9)
DimPlot(sce1, reduction = 'tsne',label=TRUE)

#Basal/intermediate
FeaturePlot(sce1, features = c( "KRT5","KRT14","KRT19","TP63"))
#CELL CYCLE
FeaturePlot(sce1, features = c( "CCNB1","CENPF","PTTG1","CDC20"))
```


Fibroblast cell
```{r}
sce3 = pbmc[, Idents(pbmc) %in% c( "Fibroblast")]
sce3 <- NormalizeData(sce3, normalization.method = "LogNormalize", scale.factor = 1e4) 
sce3 <- FindVariableFeatures(sce3, selection.method = 'vst', nfeatures = 2000)
all.genes <- rownames(sce3)
sce3 <- ScaleData(sce3,features = all.genes)

sce3 <- RunPCA(sce3, features = VariableFeatures(object = sce3))

sce3 <- FindNeighbors(sce3, dims = 1:9)
sce3 <- FindClusters(sce3, resolution = 0.15)
# Look at cluster IDs of the first 5 cells

sce3 <- RunTSNE(sce3, dims = 1:9)
DimPlot(sce3, reduction = 'tsne')

FeaturePlot(sce3, features = c( "FAP","S100A4","SPARC","ACTA2","PDGFRA","PDGFRB","CAV1","VIM"))
```


Endothelial cell
```{r}
sce4 = pbmc[, Idents(pbmc) %in% c( "Endothelial")]
sce4 <- NormalizeData(sce4, normalization.method = "LogNormalize", scale.factor = 1e4) 
sce4 <- FindVariableFeatures(sce4, selection.method = 'vst', nfeatures = 2000)
all.genes <- rownames(sce4)
sce4 <- ScaleData(sce4,features = all.genes)

sce4 <- RunPCA(sce4, features = VariableFeatures(object = sce4))

sce4 <- FindNeighbors(sce4, dims = 1:9)
sce4 <- FindClusters(sce4, resolution = 0.1)

sce4 <- RunTSNE(sce4, dims = 1:9)
DimPlot(sce4, reduction = 'tsne')

#gene markers
FeaturePlot(sce4, features = c( "PECAM1","FLT1","PDPN","S100A4","THY1","ACTA2"))

#aEC
VlnPlot(sce4, features = c("S100A4","THY1","ACTA2"))

```

Annotate Endothelial cells
```{r}
new.cluster.ids <- c("Endothelial","aEC","aEC","aEC","Endothelial","Endothelial")
names(new.cluster.ids) <- levels(sce4)
sce4 <- RenameIdents(sce4, new.cluster.ids)
sce4 <- RunTSNE(sce4, dims = 1:9)
DimPlot(sce4, reduction = "tsne", label = TRUE)
sce4@active.ident
sce4[["Annotation"]] <- sce4@active.ident
sce4@meta.data
```


Cell communication by cellphoneDB
prepare files needed
```{r}
# create count.txt file
write.table(as.matrix(pbmc@assays$RNA@data), 'data.txt', sep='\t', quote=F)

meta_data <- cbind(rownames(pbmc@meta.data), pbmc@meta.data[,'Annotation', drop=F])  
meta_data <- as.matrix(meta_data)
#create meta txt file
write.table(meta_data, 'meta.txt', sep='\t', quote=F, row.names=F)

library(psych)
library(qgraph)
library(igraph)
library(tidyverse)
```






